\vskip-0.6in Endogenous Politics and the Design of Trade Institutions

### 2016-07-25 feedback.tex
complete integration of feedback into to-do

\subsection{From SITE 2016 presentation}
\begin{itemize}
	\item Kyle: McLaren in his chapter calls the Grossman and Helpman setup with contributions 'felonious'
	\item Kyle: why doesn't government (dis)value expenditure by lobby? Needs to be counted in government welfare function or justify why not
		\begin{itemize}
			\item Rohan: $(1-a)\cdot C + a \cdot W \equiv C + a \cdot (W-C)$
			\item When weights on $\pi_X$ are not linear, what are the implications for resource waste? Is it the same as $+ C / - C$?
			\item Devashish: Utility fcn didn't change. Just got evaluated at a different point
				\begin{itemize}
					\item Preferences don't change. It's persuasion that affects decision-making. 2nd story: Giovanni's
					\item Find something in persuasion literature
				\end{itemize}
		\end{itemize}
	\item $\ga(e)$
		\begin{itemize}
			\item Giovanni: think of expost $\ga(e)$ as effort to elect/choose ex-post decision-maker
			\item At worst, I can use leg / exec split to deal with this criticism
			\item Kyle (???): advertising paper (???)
			\item Mostafa, Nuno, Giovanni, Anson to some extent: Cardinal vs. ordinal
				\begin{itemize}
					\item Giovanni: if I can show properties survive  monotonic transformation, I'm fine
					\item They don't like gov't choosing its own preferences. May just need to change wording
				\end{itemize}
			\item Bob: what is fundamental structure of preferences?
			\item The way $e$ affects preferences doesn't change!!! Preferences are wrapped up in $\ga$!
		\end{itemize}
	\item Bob: maybe gov't has some other reason for setting non-zero tariff that opens the door for lobbies. 2nd best remedy for market failure, etc.
		\begin{itemize}
			\item Maybe I should just get rid of tariff cap result altogether
		\end{itemize}
	\item David DeRemer: Safeguards have dropped off in use around the world
		\begin{itemize}
			\item Look at U.S. vs. ROW (he sent papers)
		\end{itemize}
	\item I think that I need to bring people along more carefully from GH/MRC to what I'm doing
	\item Bob and Kyle: take my time, make it as good as possible. Better to have quality.
\end{itemize}

>>>>

\subsection{From SITE 2016 presentation}
\begin{itemize}
	\item Kyle: McLaren in his chapter calls the Grossman and Helpman setup with contributions 'felonious' [in to-do list]
	\item Kyle: why doesn't government (dis)value expenditure by lobby? Needs to be counted in government welfare function or justify why not [in to-do list]
		\begin{itemize}
			\item Rohan: $(1-a)\cdot C + a \cdot W \equiv C + a \cdot (W-C)$
			\item When weights on $\pi_X$ are not linear, what are the implications for resource waste? Is it the same as $+ C / - C$?
			\item Devashish: Utility fcn didn't change. Just got evaluated at a different point
				\begin{itemize}
					\item Preferences don't change. It's persuasion that affects decision-making. 2nd story: Giovanni's
					\item Find something in persuasion literature
				\end{itemize}
		\end{itemize}
	\item $\ga(e)$ [in to-do list]
		\begin{itemize}
			\item Giovanni: think of expost $\ga(e)$ as effort to elect/choose ex-post decision-maker
			\item At worst, I can use leg / exec split to deal with this criticism
			\item Kyle (???): advertising paper (???)
			\item Mostafa, Nuno, Giovanni, Anson to some extent: Cardinal vs. ordinal
				\begin{itemize}
					\item Giovanni: if I can show properties survive  monotonic transformation, I'm fine
					\item They don't like gov't choosing its own preferences. May just need to change wording
				\end{itemize}
			\item Bob: what is fundamental structure of preferences?
			\item The way $e$ affects preferences doesn't change!!! Preferences are wrapped up in $\ga$!
		\end{itemize}
	\item Bob: maybe gov't has some other reason for setting non-zero tariff that opens the door for lobbies. 2nd best remedy for market failure, etc. [in to-do list]
		\begin{itemize}
			\item Maybe I should just get rid of tariff cap result altogether
		\end{itemize}
	\item David DeRemer: Safeguards have dropped off in use around the world [in to-do list]
		\begin{itemize}
			\item Look at U.S. vs. ROW (he sent papers)
		\end{itemize}
	\item I think that I need to bring people along more carefully from GH/MRC to what I'm doing
	\item Bob and Kyle: take my time, make it as good as possible. Better to have quality.
\end{itemize}

### 2016-07-25 to-do.tex
move one point from Ben's feedback into to-do
complete integration of feedback into to-do

\section{Misc.}
\begin{itemize}
	\item Define $\ga$ before using it
	\item If add back in assumption 1, add Ethier footnote
	\item standardize $\ga(e,s)$, $\ga(e)$, $\ga(s)$ throughout the text
	\item Peter: $\ga(e)$ and $\ga(s)$ combination is interesting, so it dyanmic choice of protection over time, gov't turnover [add to conclusion, it's in slides]
\end{itemize}

\section{Deal with ``dynamic preferences'' issue}
	\begin{itemize}
		\item James: need to be more precise about when $\ga$ is evaluated
			\begin{itemize}
				\item Skeptical of comparative-static style result: can I really compare governments with different $\ga$'s?
			\end{itemize}
		\item References from Krishna and Sadowski (2014) ECTA
				\begin{itemize}
					\item DILLENBERGER, D., J. S. LLERAS, P. SADOWSKI, AND N. TAKEOKA (2013): ``A Theory of Subjective Learning,'' Working Paper. 
					\item GUL, F., AND W. PESENDORFER (2004): ``Self-Control and the Theory of Consumption,'' Econometrica, 72 (1), 119-158
					\item JONES, R. A., AND J. M. OSTROY (1984): ``Flexibility and Uncertainty,'' Review of Economic Studies, 51 (1), 13-32
					\item KOOPMANS, T. C. (1964): ``On the Flexibility of Future Preferences,'' in Human Judgments and Optimality, ed. by M. W. Shelly and G. L. Bryan. New York: Wiley.
					\item KREPS, D. M., AND E. L. PORTEUS (1978): ``Temporal Resolution of Uncertainty and Dynamic Choice Theory,'' Econometrica, 46 (1), 185-200.
				\end{itemize}
		\end{itemize}
\section{Take out repeats}
	Especially of references to BS2005: In some parts the paper also seem repeating itself: you review Bagwell and Staiger (2005) in Section 2.2 but you provide another summary of the same paper in Section 3. Again, a revised structure may reduce the overlap, make the paper shorter, and be more to the point.

@@

\section{Lit review}
\begin{itemize}
	\item Find MRC cites (maybe some in Ethier) for why PE shocks can't be addressed
		\begin{itemize}
			\item Bagwell and Staiger 1999 AER
		\end{itemize}
	\item Have to make connection to endogenous papers clearer
		\begin{itemize}
			\item and make clear that GH is isomorphic / provides microfoundations for Baldwin objective function
			\item More on Coates $\&$ Ludema (2001)
		\end{itemize}
	\item Paola: How do I want to sell the paper?
		\begin{itemize}
			\item In relation to what literature?
				\begin{itemize}
					\item What literature does endogenous? Coates-Ludema 2001, MRC, GH
					\item What literature \textit{doesn't}?
				\end{itemize}
			\end{itemize}
	\item Review Bown, Bagwell $\&$ Staiger
	\item Do I include papers like BS2001 (non-repeated) in lit review?
	\item Read Rosendorff $\&$ Milner (2001) [from Cristiane Carneiro at PEIO]
	\item Limao and Tovar 2011
		\begin{enumerate}
			\item Their 2nd (and final) stage is Nash bargaining. Is there an isomorphism to my setup?
			\item It IS clear to take their first, limited case of commitment to tariff cap only (ignore NTB) as analogy for gov't in my model choosing commitment to different tariff level. Need to answer Q1 above in order to answer points 3 and 4:
			\item Their gains from commitment derive from improvement in bargaining power vis-a-vis the lobby (Schelling conjecture invoked). How does this relate to the gain from commitment in my model?
			\item Top of page 6: ``large enough bargaining power.'' Can I make connection to $\ga(e)$?
			\item Note: in their equation 3, $C$ enters expression for NBS's ($\tau$) in equilibrium, it doesn't disappear as in GH
		\end{enumerate}
\end{itemize}

\section{Clarify information structure}

@@

\section{Lobbying cost included in gov't welfare}
	\begin{itemize}
		\item Rick Bond: need lobbying to use up resources: if it changes net profits, it should also change $\pi$ in $W(\tau,\tau^*)$
	\end{itemize}
\end{document}

>>>>

\section{Misc.}
\begin{itemize}
	\item Define $\ga$ before using it
	\item If add back in assumption 1, add Ethier footnote
	\item standardize $\ga(e,s)$, $\ga(e)$, $\ga(s)$ throughout the text
	\item Peter: $\ga(e)$ and $\ga(s)$ combination is interesting, so it dyanmic choice of protection over time, gov't turnover [add to conclusion, it's in slides]
	\item Ben: I'm wondering how you view the time-frame over which your model is set.  On one hand a specific-factors set-up is normally associated with the short-run.  But on the other hand you have an infinite time horizon which suggests very long run.
	\item Clarify information structure

\section{Deal with ``dynamic preferences'' issue}
	\begin{itemize}
		\item James: need to be more precise about when $\ga$ is evaluated
			\begin{itemize}
				\item Skeptical of comparative-static style result: can I really compare governments with different $\ga$'s?
			\end{itemize}
		\item References from Krishna and Sadowski (2014) ECTA
				\begin{itemize}
					\item DILLENBERGER, D., J. S. LLERAS, P. SADOWSKI, AND N. TAKEOKA (2013): ``A Theory of Subjective Learning,'' Working Paper. 
					\item GUL, F., AND W. PESENDORFER (2004): ``Self-Control and the Theory of Consumption,'' Econometrica, 72 (1), 119-158
					\item JONES, R. A., AND J. M. OSTROY (1984): ``Flexibility and Uncertainty,'' Review of Economic Studies, 51 (1), 13-32
					\item KOOPMANS, T. C. (1964): ``On the Flexibility of Future Preferences,'' in Human Judgments and Optimality, ed. by M. W. Shelly and G. L. Bryan. New York: Wiley.
					\item KREPS, D. M., AND E. L. PORTEUS (1978): ``Temporal Resolution of Uncertainty and Dynamic Choice Theory,'' Econometrica, 46 (1), 185-200.
				\end{itemize}
			\item Giovanni: think of expost $\ga(e)$ as effort to elect/choose ex-post decision-maker
			\item At worst, I can use leg / exec split to deal with this criticism
			\item Kyle (???): advertising paper (???)
			\item Mostafa, Nuno, Giovanni, Anson to some extent: Cardinal vs. ordinal
				\begin{itemize}
					\item Giovanni: if I can show properties survive  monotonic transformation, I'm fine
					\item They don't like gov't choosing its own preferences. May just need to change wording
				\end{itemize}
			\item Bob: what is fundamental structure of preferences?
			\item The way $e$ affects preferences doesn't change!!! Preferences are wrapped up in $\ga$!
		\end{itemize}
	Bob: maybe gov't has some other reason for setting non-zero tariff that opens the door for lobbies. 2nd best remedy for market failure, etc.
	\begin{itemize}
			\item Maybe I should just get rid of tariff cap result altogether [me]
		\end{itemize}
\section{Take out repeats}
	Especially of references to BS2005: In some parts the paper also seem repeating itself: you review Bagwell and Staiger (2005) in Section 2.2 but you provide another summary of the same paper in Section 3. Again, a revised structure may reduce the overlap, make the paper shorter, and be more to the point.

@@

\section{Lit review}
\begin{itemize}
	\item Find MRC cites (maybe some in Ethier) for why PE shocks can't be addressed
		\begin{itemize}
			\item Bagwell and Staiger 1999 AER
		\end{itemize}
	\item Have to make connection to endogenous papers clearer
		\begin{itemize}
			\item and make clear that GH is isomorphic / provides microfoundations for Baldwin objective function
			\item More on Coates $\&$ Ludema (2001)
		\end{itemize}
	\item I think that I need to bring people along more carefully from GH/MRC to what I'm doing
	\item Paola: How do I want to sell the paper?
		\begin{itemize}
			\item In relation to what literature?
				\begin{itemize}
					\item What literature does endogenous? Coates-Ludema 2001, MRC, GH
					\item What literature \textit{doesn't}?
				\end{itemize}
			\end{itemize}
	\item Review Bown, Bagwell $\&$ Staiger
	\item Do I include papers like BS2001 (non-repeated) in lit review?
	\item Read Rosendorff $\&$ Milner (2001) [from Cristiane Carneiro at PEIO]
	\item Kyle: McLaren in his chapter calls the Grossman and Helpman setup with
	 contributions 'felonious'
	\item David DeRemer: Safeguards have dropped off in use around the world
		\begin{itemize}
			\item Look at U.S. vs. ROW (he sent papers)
		\end{itemize}
	\item Limao and Tovar 2011
		\begin{enumerate}
			\item Their 2nd (and final) stage is Nash bargaining. Is there an isomorphism to my setup?
			\item It IS clear to take their first, limited case of commitment to tariff cap only (ignore NTB) as analogy for gov't in my model choosing commitment to different tariff level. Need to answer Q1 above in order to answer points 3 and 4:
			\item Their gains from commitment derive from improvement in bargaining power vis-a-vis the lobby (Schelling conjecture invoked). How does this relate to the gain from commitment in my model?
			\item Top of page 6: ``large enough bargaining power.'' Can I make connection to $\ga(e)$?
			\item Note: in their equation 3, $C$ enters expression for NBS's ($\tau$) in equilibrium, it doesn't disappear as in GH
		\end{enumerate}
\end{itemize}

@@

\section{Lobbying cost included in gov't welfare}
	\begin{itemize}
		\item Rick Bond: need lobbying to use up resources: if it changes net profits, it should also change $\pi$ in $W(\tau,\tau^*)$
		\item Kyle: why doesn't government (dis)value expenditure by lobby? Needs to be counted in government welfare function or justify why not
		\begin{itemize}
			\item Rohan: $(1-a)\cdot C + a \cdot W \equiv C + a \cdot (W-C)$
			\item When weights on $\pi_X$ are not linear, what are the implications for resource waste? Is it the same as $+ C / - C$?
			\item Devashish: Utility fcn didn't change. Just got evaluated at a different point
				\begin{itemize}
					\item Preferences don't change. It's persuasion that affects decision-making. 2nd story: Giovanni's
					\item Find something in persuasion literature
				\end{itemize}
		\end{itemize}
	\end{itemize}
\end{document}
